Verifying Spatial Properties of Array Computations

### 2017-04-15 oopsla17/oopsla17.tex
Restore singletons in subscripts scheme

\begin{defn}[Interval scheme]
  An interval scheme is a finite Cartesian product of intervals on
  \bz{} or \bz{} itself, 
  denoted by the set $\textit{Interval}^N$ for a product of $N$ intervals.
\end{defn}

\begin{defn}[Subscript scheme]
  A $N$-dimensional \emph{subscript scheme} is an $N$-dimensional
  interval scheme where:
  %
  \begin{equation*}
    \forall i.\ 1 \leq i \leq N \implies
      \pi_i (S) = [p, p] 
      \; \vee \;
      \pi_i (S) = \bz{}
    \end{equation*}
    That is, the $i^{th}$ component of the set is either a singleton
  in $\mathbb{Z}$ or the infinite interval.
\end{defn}
%
\dnote{May want a predicate as well}

>>>>

\begin{defn}[Interval scheme]
  An interval scheme is a finite Cartesian product of intervals on \bz{},
  denoted by the set $\textit{Interval}^N$ for a product of $N$ intervals.
\end{defn}

\begin{defn}[Subscript scheme]
  A \emph{subscript scheme} is an index scheme scheme where:
  %
  \begin{equation*}
    \forall i.\ 1 \leq i \leq N \implies
      \pi_i (S) = \{ p \}
      \; \vee \;
      \pi_i (S) = [-\infty, \infty]
    \end{equation*}
%
  That is, the $i^{th}$ component of the set is either a singleton in \bz{} or
  the infinite interval.
\end{defn}
%
\dnote{May want a predicate as well}
